---
title: 'IGHV1-24'
execute:
  echo: false
format: html
server: shiny
---
```{r}
source("functions.R")
```

```{r, echo=FALSE}
load("data.rda")

chain = "IGH"
func <-  data.frame(allele = names(vgerms[[chain]]), functionality = T, sign = 'F', stringsAsFactors = F)

mat <- mat_list$IGH$functional$nonsingle$all$`318`

load("data_frac_new2.rda")
data <- setDT(data_frac$IGH$functional$nonsingle$all$`318`$complete$`95`)
data[,v_call:=paste0(v_gene,"*",v_allele)]
load("alleles_dbs.rda")
allele_db <- alleles_dbs$IGH$functional$nonsingle$all$`318`$complete$`95`
allele_db <- allele_db %>% dplyr::rowwise() %>% dplyr::mutate(gene = alakazam::getGene(or_allele, strip_d = F, omit_nl = F), group = strsplit(gsub(gene, "", new_allele),"[*]")[[1]][1], gene_group = alakazam::getGene(new_allele, strip_d = F, omit_nl = F))
load("functional_groups.rda")
func_groups <- functional_groups$IGH$functional$nonsingle$all$`318`$complete$`95`

cols <- c("#FAAB18", "#1380A1","#990000", "#588300")

pal <- cols %>% 
  newpal(names = c("orangy", "bluish", "redish", "greeny"))

edit_links <- readLines("edit_links.txt")
share_links <- readLines("share_links.txt")
```

```{r,echo=FALSE}
g_group = 'IGHV1-24G3'
group = names(func_groups)[func_groups==g_group]
gr <- allele_db %>% filter(gene_group == g_group) %>% pull(group) %>% unique()
g <- allele_db %>% filter(gene_group == g_group) %>% pull(gene) %>% unique()
```

## Allele appearnce 

The group of `r group` includes `r length(grep(g_group,allele_db$new_allele,value=T))` alleles, `r sum(func$functionality[func$allele %in% allele_db$or_allele[grep(g_group,allele_db$new_allele)]])` out of the alleles are functional.

For each allele we counted the number of appearances across the population, any appearance was considered valid. 

```{r}
allele_appearance(data, g_group, allele_db)
```

## Sequence depth

To examine the potential cutoff we observed the sequence depth for each allele

```{r}
tagList(sequence_depth(data, g_group, allele_db))
```

## Conclusions

Because we observed a single allele in this group we set the cutoff to $0.01%$ absolute threshold (the relative repertoire frequency). The plot below shows the frequency of the group above the threshold line.

```{r, out.height= "100%", out.width="100%"}
m <- list(
    l = 50,
    r = 50,
    b = 100,
    t = 100,
    pad = 0.5
)
heatmap_alleles(data, g_group, allele_db, func)%>%
  layout(autosize = F, width = 800, height = 1300)
```
